Untitled

### 2020-06-26 R/model.Rmd
updated location of rf model

---
title: "Untitled"
author: "Betty Kreakie"
date: "April 25, 2019"
output: html_document
---

@@

# B: I'm saving a copy of the model for later use.  It is too big to github so i added it to .gitignore
saveRDS(RFAll, here::here('data/RFAll20190503.Rds'))
```

>>>>

---
title: "Untitled"
author: "Betty Kreakie"
date: "April 25, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

# B: I'm saving a copy of the model for later use.  It is too big to github so i added it to .gitignore
saveRDS(RFAll, "L:/Public/Milstead_Lakes/prism/RFAll20190503.Rds")
```
